### 2019-06-07 paper_05_milestone_issf/article.tex
Fix for long author list add et al.

\begin{figure}[htb]
\centerline{
\includegraphics[width=10cm]{Figures/scheme_exp_grid_MILESTONE_Euhit.pdf}}
\vspace{5mm}
\centerline{
\includegraphics[width=80mm]{Figures/GOPR1453.pdf}
\includegraphics[width=80mm]{Figures/fig_movement_carriage.pdf}}
\caption{Top: scheme of the experimental setup (see text for
description). Bottom left: photography of the experiment. Two of our cameras
are visible (highlighted in red), the third one being below the window
highlighted by the black rectangle. Three of our five probes are highlighted in
blue, $P_c$ is embarked on the carriage and $P_p^1$ and $P_p^2$ are attached to
profilers. The vertical PIV field of view and its associated cameras are not
visible in the photo. Bottom right: chronogram of the position of the carriage
$x_c(t)$.}
\label{fig:exp}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=16cm]{Figures/fig_profiles.pdf}}
\vspace{-2mm}
\caption{Left: density profiles for $N=0.8$ rad/s and $U_c = 6$ cm/s. Right:
variations of density with respect to the profile at rest
$\Delta\rho=\rho-\rho(t/T=-0.13)$.}
\label{fig_profiles}
\end{figure}

@@

\input{table.tex}

@@

\begin{figure}[htb]
\centerline{
\includegraphics[width=5.18cm]{\pathfigures/exp21/vh_400.pdf}
\includegraphics[width=4.3cm]{\pathfigures/exp21/vh_655.pdf}
\includegraphics[width=5.9cm]{\pathfigures/exp21/vh_890.pdf}}
\vspace{0mm}
\centerline{
\includegraphics[width=5.2cm]{\pathfigures/exp21/vv_890.pdf}
\includegraphics[width=4.35cm]{\pathfigures/exp21/vv_655.pdf}
\includegraphics[width=5.8cm]{\pathfigures/exp21/vv_400.pdf}
}
\vspace{-2mm}
\caption{Instantaneous horizontal large fields (top, $z=40$~cm) and vertical
fields (bottom) for $t/T = [1.31,~1.5,~1.68]$, $F_{hc} = 0.1$ and
$\mathcal{R}_c=450$. Background colors indicate the norm of the 2D field
normalized by $U_c$, which is $(u_x^2 + u_y^2)/U_c$ and $(u_x^2 + u_z^2)/U_c$,
respectively.}
\label{fig:field}
\end{figure}

@@

\begin{figure}[htb]
\centerline{\includegraphics[width=9.cm]%
{\pathfigures/exp28/ken_fct_t_T_exp28.pdf}}
\vspace{-2mm}
\caption{Spatial average of normalized horizontal kinetic energy
$\langle u_x^2 + u_y^2\rangle/2U_c^2$ as a function of the fractional part of
the normalized time $\{t/T\}$ for different periods of measurement and for
$F_{hc} = 0.1$ and $\mathcal{R}_c=450$. Times where no data appears corresponds
to those when the carriage is in the field of view and hides a part of the
field of view. The gray line represents the position of the carriage $x_c$ and
the three red circles mark the times chosen for the figure~\ref{fig:field}. The
pair of symbols $\vartriangleleft-\vartriangleright$ delimits the ranges of
time where the carriage appears in the field of view.}
\label{fig:ken}
\end{figure}

\noindent We now characterize the distribution of energy among scales by second-order
structure function, defined as
\begin{eqnarray}
S_h(r) = (S_{xx} + S_{yy} + S_{xy} + S_{yx})/2,\\
\text{with} \quad S_{ij} = \langle\overline{(u_i({\bf x}+r{\bf e}_j)-u_i({\bf x}))^2}\rangle,
\end{eqnarray}
and $\overline{\cdot}$ time average when the carriage is moving. For a
developed turbulence, and for scales larger than the dissipative scale and
lower than injection scale, we expect
$S_h(r) = C (\varepsilon r)^{2/3} = C' (rU_c^3/M)^{2/3}$, with $C$ a coefficient
approximately equal to 6 \cite[see figure 15 in][]{AugierBillantChomaz2015}.
\begin{figure}[htb]
\centerline{\includegraphics[height=7.5cm]%
{\pathfigures/exp28/normalized_S2_exp28.pdf}}
\vspace{-2mm}
\caption{Normalized second-order structure $S_h$ function as a function of
$r/M$ for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$.}
\label{fig:S2}
\end{figure}
Figure~\ref{fig:S2} represents normalized second-order structure function
computed from large horizontal fields for a 12 periods forcing
experiment. Interestingly, the curve exhibits a plateau corresponding to a
$r^{2/3}$ scaling law on half a decade at a value going from $0.4$ at
$\{t/T\} = 0.31$ to $0.2$ at $\{t/T\} = 0.31$. Supposing that this range
corresponds to an inertial range, we evaluate a surrogate of the mean
dissipation rate at $\epsK \sim 0.01 U_c^3/M$. This order of magnitude is
consistent with the previous estimation by direct computation of the energy
decay.

>>>>

\begin{figure}[htb]
\centerline{
\includegraphics[width=10cm]{Figures/scheme_exp_grid_MILESTONE_Euhit.pdf}}
\vspace{5mm}
\centerline{
\includegraphics[width=0.45\textwidth]{Figures/GOPR1453.pdf}
\includegraphics[width=0.45\textwidth]{Figures/fig_movement_carriage.pdf}}
\caption{Top: scheme of the experimental setup (see text for
description). Bottom left: photography of the experiment. Two of our cameras
are visible (highlighted in red), the third one being below the window
highlighted by the black rectangle. Three of our five probes are highlighted in
blue, $P_c$ is embarked on the carriage and $P_p^1$ and $P_p^2$ are attached to
profilers. The vertical PIV field of view and its associated cameras are not
visible in the photo. Bottom right: chronogram of the position of the carriage
$x_c(t)$.}
\label{fig:exp}
\end{figure}

\begin{figure}
\centerline{\includegraphics[]{Figures/fig_profiles.pdf}}
\vspace{-2mm}
\caption{Left: density profiles for $N=0.8$ rad/s and $U_c = 6$ cm/s. Right:
variations of density with respect to the profile at rest
$\Delta\rho=\rho-\rho(t/T=-0.13)$.}
\label{fig_profiles}
\end{figure}

@@

\input{paper_05_milestone_issf/table.tex}

@@

\begin{figure}[htb]
\centerline{
\includegraphics[width=4.14cm]{paper_05_milestone_issf/Figures/exp21/vh_400.pdf}
\includegraphics[width=3.44cm]{paper_05_milestone_issf/Figures/exp21/vh_655.pdf}
\includegraphics[width=4.72cm]{paper_05_milestone_issf/Figures/exp21/vh_890.pdf}}
\vspace{0mm}
\centerline{
\includegraphics[width=4.16cm]{paper_05_milestone_issf/Figures/exp21/vv_890.pdf}
\includegraphics[width=3.48cm]{paper_05_milestone_issf/Figures/exp21/vv_655.pdf}
\includegraphics[width=4.63cm]{paper_05_milestone_issf/Figures/exp21/vv_400.pdf}
}
\vspace{-2mm}
\caption{Instantaneous horizontal large fields (top, $z=40$~cm) and vertical
fields (bottom) for $t/T = [1.31,~1.5,~1.68]$, $F_{hc} = 0.1$ and
$\mathcal{R}_c=450$. Background colors indicate the norm of the 2D field
normalized by $U_c$, which is $(u_x^2 + u_y^2)/U_c$ and $(u_x^2 + u_z^2)/U_c$,
respectively.}
\label{fig:field}
\end{figure}

@@

\begin{figure}[htb]
\centerline{
\includegraphics[width=9.cm]{paper_05_milestone_issf/Figures/exp28/ken_fct_t_T_exp28.pdf}}
\vspace{-2mm}
\caption{Spatial average of normalized horizontal kinetic energy
$\langle u_x^2 + u_y^2\rangle/2U_c^2$ as a function of the fractional part of
the normalized time $\{t/T\}$ for different periods of measurement and for
$F_{hc} = 0.1$ and $\mathcal{R}_c=450$. Times where no data appears corresponds
to those when the carriage is in the field of view and hides a part of the
field of view. The gray line represents the position of the carriage $x_c$ and
the three red circles mark the times chosen for the figure~\ref{fig:field}. The
pair of symbols $\vartriangleleft-\vartriangleright$ delimits the ranges of
time where the carriage appears in the field of view.}
\label{fig:ken}
\end{figure}

\noindent We now characterize the distribution of energy among scales by second-order
structure function, defined as
\begin{eqnarray}
S_h(r) = (S_{xx} + S_{yy} + S_{xy} + S_{yx})/2,\\
\text{with} \quad S_{ij} = \langle\overline{(u_i({\bf x}+r{\bf e}_j)-u_i({\bf x}))^2}\rangle,
\end{eqnarray}
and $\overline{\cdot}$ time average when the carriage is moving. For a
developed turbulence, and for scales larger than the dissipative scale and
lower than injection scale, we expect
$S_h(r) = C (\varepsilon r)^{2/3} = C' (rU_c^3/M)^{2/3}$, with $C$ a coefficient
approximately equal to 6 \cite[see figure 15 in][]{AugierBillantChomaz2015}.
\begin{figure}[htb]
\centerline{
\includegraphics[height=7.5cm]{paper_05_milestone_issf/Figures/exp28/normalized_S2_exp28.pdf}}
\vspace{-2mm}
\caption{Normalized second-order structure $S_h$ function as a function of
$r/M$ for $F_{hc} = 0.1$ and $\mathcal{R}_c=450$.}
\label{fig:S2}
\end{figure}
Figure~\ref{fig:S2} represents normalized second-order structure function
computed from large horizontal fields for a 12 periods forcing
experiment. Interestingly, the curve exhibits a plateau corresponding to a
$r^{2/3}$ scaling law on half a decade at a value going from $0.4$ at
$\{t/T\} = 0.31$ to $0.2$ at $\{t/T\} = 0.31$. Supposing that this range
corresponds to an inertial range, we evaluate a surrogate of the mean
dissipation rate at $\epsK \sim 0.01 U_c^3/M$. This order of magnitude is
consistent with the previous estimation by direct computation of the energy
decay.
